\section{Introduction}
General introduction to EIT itself, the village/topic and then to our specific project and our motivation behind it.

Introductions of our persons:

\begin{itemize}
    \item \textbf{Dauderis, Astrid}\\
    I am a 26 year old woman from northern Norway. I am currently in my 3rd year of studying clinical psychology at NTNU. I have previously studied 2 years of psychology at UiT, where I also exchanged to Aarhus, Denmark.\\
    In between these studies I worked in residental care for children, for two years. We worked in teams, and my coworkers came from a diversity of academic backgrounds. 
    Now I am working for a NTNU research project about head injuries, where I carry out neuropsychological testing.\\
    I have a strong interest in environmently friendly living and sustainability, which is why I chose this village. 
    \item \textbf{Müller, Florian}\\
    My background is classic Mechanical Engineering (graduated 2011).
    After university I started working in a company (300 employees) building electrical generators for power plants.
    This company was embedded in a US based corporation (35.000 employees).
    I have worked in highly diverse teams and went through various mandatory diversity and team building methods.\\
    I started studying at NTNU as part of my 2 year masters programme "RAMS" (Reliability, Availability, Maintainability, Safety) in August 2015.\\
    Sustainability is a key interest of mine and I picked that village to contribute with my academic and worklife experience.
    At the end of that semester I will turn 29 and I have one older sister.
    \item \textbf{Schikora, Stian}\\
    I am currently enrolled in the master program in nanotechnology at NTNU and will be graduating in 2017. During my masters i have been quite active in our student union (TIMINI) and also spent one year as the leader for study programs academic team, which is mainly responsible for the quality assurance of the program. Through this i have gotten experienced in teamwork. During the last years i have some work experience working av a teaching assistant in several courses which has improved my theoretical knowledge.
    I am born and raised in Lørenskog in Norway and I am an only child with no siblings. In the summer i will turn 24.
    \item \textbf{Tarimo, Michael}\\
    I'm a Tanzanian Civil and Structural Engineer graduated at University of Dar es Salaam August 2009.After Graduation I worked with Send Star Construction Company for 6 months as Site Engineer then i joined Saifee Structural Engineers Consultant from March 2010 to November 2010 as Design Engineer. From December 2010 to date I'm an employee of Tanzania National Parks as a Civil Engineer and my duty station is The Serengeti National Park.
    I'm currently studying my 2 years Masters in Project Management since August 2015.
    I'm 36 years old married and i have 3 children two daughters and one son and I also have 3 sisters.
    Due to the nature of my working environment which is World Heritage site protected area, Environmental sustainability is my first priority consideration in order to preserve the wild areas for the future generation.
    
    \item \textbf{Thapa, Bikash}\\
    I am currently doing my Masters in Hydropower Development from NTNU which is of two years course. I am 25 years old and I did my Bachelors in 2013 in Civil Engineering from Kathmandu University, Nepal. After my Bachelors, I worked as a Teaching Assistant for 2 years in the same University. I also worked as a partt time engineer in a consultancy form that deals with design and survey of micro hydropower projects in Nepal for six months. 
    \item \textbf{Torres Caceres, Veronica A.}\\
    I graduated as Geophysical Engineering in December 2010 from Universidad Central de Venezuela (UCV). I worked for 1 year and 3 months in IHS (US company) as technical support for Kingdom Suit software (Seismic Interpretation software) and then I moved to Mexico and I worked 2 year and 8 months for PGS (Norwegian Company) as a Seismic Interpreter and Geophysicist. This job helped me to be more involved in a multidisciplinary and multicultural work environment and get in touch with the latest seismic processing and acquisition technologies directly related to the Oil and Gas industry.\\
    I am currently doing a Master Degree at NTNU in Petroleum Geophysics, since August 2015. \\
    I am 28 years old and I have a brother who is 3 years older than me. 
    
\end{itemize}

