\section{Triangle of Confidence}

Qualities

BT
Organized
Always been expecting perfections in work
Check


SRS
I see myself as an optimistic person
Check


AGD
I am creative.
Check

SRS
I'm a good team player and listener.
Quality develop through being a board member in the student union and also being the leader of the study program's academic team
Check

VT
Responsible
Check




MJ
Cost consious

MJ
Hard worker
How I was raised by parents

FM
I can communicate technical problems to non-technical persons
I have a mother

AGD
I'm honest

AGD
I am very fair.

FM
I'm calm
I have enough awareness that anger never helps

FM
I can understand and read into technical subjects quite fast
I have a wide interest in almost all engineering fields


BT
Well-planned
Always want to work step by step making schedules and plans

BT
Good listener
I can listen to others without being restless for long time (Even if it is not of my interest - just for others sake) (since childhood)

SRS
I'm easy to work with!


VT
I am proactive person

VT
I am perfectionist person




Area of Knowledge

AGD
Psychology
I have always had an interest for it and have studied it for 5 years.
Check


FM
Mechanical Engineering allows me to evaluate all kind of technical approaches
B.Eng.
Check

AGD
Environmentally friendly solutions
I've had an interest in the environment from an early age, and try to keep updated on what I can contribute with
Check

MJ
Construction of Houses
Construction of Roads
Construction of Bridges and Culverts
Design of Structures
Doing Drawings
BG: Civil Engineering
Check

BT
Project Work
Have done several projects on Bachelor and also supervised student project when I was working as teaching assistant


BT
Hydropower Engineering
Area of expertise in bachelor and masters


SRS
I have knowledge within Mathematics, statistics and also modelling using these tools
NTNU


SRS
I have knowledge about basic chemical handling and organic chemistry.
This knowledge has been attained through courses at NTNU

MJ
Supervision of construction projects
Experience

VT
I have knowledge in subsurface quality factor for constructions (Seismology)



VT
I have knowledge in geology
Studied it in my bachelor

FM
Risk and Safety analysis
My RAMS Master program


AGD
Research (and SPSS)
My job.

FM
Electricity production and distribution
Working in a relevant company

SRS
I have knowledge about MEMS manufacturing and usage (Sensors, actuators, etc. )
Attained through courses at NTNU

VT
I have knowledge in physics and mathematics
I'm an Engineer


BT
Construction materials
Studied during Bachelor and also worked for a while.



Skills

BT
Use of different softwares for documentation, drawings and design
Using different softwares since schooling

VT
I am good at paying attention to details
My dad always encouraged me to do it
Check

FM
Report writing
Wrote a lot of various reports at work and university
Check


AGD
I'm good at interacting with people
I've grown up in a big family.
Check


SRS
I'm quite skilled in time management
Had a couple of semesters where I've taken on way too much to do...
Check

FM
Good in finding academic/scientific articles
Personal experience and courses on that
Check


SRS
I'm getting quite skilled in computer programming.
Attained through numerous courses and also personal interests.


AGD
I learn easily. 
I've always been very interested in learning new things.

SRS
I have some skill in 3D-modelling
Working with 3D-printers for some time now


AGD
I'm good at working with my hands.
I've been quite creative my whole life and love diy-projects.

VT
I an god at programming
I learnt it during my bachelor and sometimes I have needed for solving problems at work

VT
I am good at calculations
I like to do it

MJ
Use of AutoCAD software
Learning / Studied

FM
I know German
Spend a few years there


MJ
Swimming
Hobby

MJ
Driving
Driving School

BT
Estimation and good with numbers (Calculations)
Engineering being my background of study

BT
Speaking in a mass of people
Working as a teaching assistant for two years in university


FM
3D CAD
Doing some CAD work at work